---
title: "Update Risk Analysis Report Test Data
date: "`r Sys.Date()`"
---

# Introduction
The purpose of this document is to document the techniques for updating the risk analysis test data used in this package. 

# Manual Export Using SQL Develoer
This section describes how to process data manually exported from SQLDeveloper. 

```{r import-libraries}
library(stringr)
library(readr)
library(DBI)
library(ROracle)
library(keyring)
```


# Automatic Update Using `ROracle`
This section describes how to make a direct connection to the project Oracle database and export the data tables from this connection. 

```{r oracle-connection}
# Use the `keyring` package to save the database username and password in the 
# system credential store
key_service <- "egis-db-brandonroad"
user_name <- "BrandonRoad"
# Set once on each computer prior to building book
# keyring::key_set(service = key_service, username = user_name)

# Make Oracle connection
drv  <- DBI::dbDriver("Oracle")
host <- "egis-db"
port <- "1521"
sid  <- "B5SDEDP1"
connect_string <- paste0(
  "(DESCRIPTION=",
  "(ADDRESS=(PROTOCOL=tcp)(HOST=", host, ")(PORT=", port, "))",
  "(CONNECT_DATA=(SID=", sid, ")))")
 
con_roracle <- ROracle::dbConnect(drv, 
                                  username = user_name, 
                                  password = key_get(key_service, user_name),
                                  dbname   = connect_string)
```

```{r import-oracle-tables, echo=FALSE, warning=FALSE, message=FALSE}
# Import tables from Oracle
db_risk              <- ROracle::dbReadTable(con_roracle, 
                                             "RISK_MAIN_VIEW")
db_events            <- ROracle::dbReadTable(con_roracle, 
                                             "EVENTS_MAIN_VIEW")
db_discussion        <- ROracle::dbReadTable(con_roracle, 
                                             "DISCUSSION_LOG_MAIN_VIEW")
db_action            <- ROracle::dbReadTable(con_roracle, 
                                             "ACTION_MAIN_VIEW")
db_decision          <- ROracle::dbReadTable(con_roracle, 
                                             "DECISION_MAIN_VIEW")
db_rel_action_action <- ROracle::dbReadTable(con_roracle, 
                                             "REL_ACTION_ACTION_MAIN_VIEW")
db_rel_dec_dec       <- ROracle::dbReadTable(con_roracle, 
                                             "REL_DEC_DEC_MAIN_VIEW")
db_rel_dec_action    <- ROracle::dbReadTable(con_roracle, 
                                             "REL_DEC_ACTION_MAIN_VIEW")
db_rel_risk_action   <- ROracle::dbReadTable(con_roracle, 
                                             "REL_RISK_ACTION_MAIN_VIEW")
db_rel_risk_dec      <- ROracle::dbReadTable(con_roracle, 
                                             "REL_RISK_DEC_MAIN_VIEW")
db_rel_risk_risk     <- ROracle::dbReadTable(con_roracle, 
                                             "REL_RISK_RISK_MAIN_VIEW")

# Disconnect from the database
ROracle::dbDisconnect(con_roracle)
```

```{r save-package-data}
usethis::use_data(db_risk,
                  db_events,
                  db_discussion,
                  db_action,
                  db_decision,
                  db_rel_action_action,
                  db_rel_dec_dec,
                  db_rel_dec_action,
                  db_rel_risk_action,
                  db_rel_risk_dec,
                  db_rel_risk_risk,
                  overwrite = TRUE)
```

