---
title: "Getting started with the `rarr` Package"
author: Barrie Chileen Martinez
date: "2023-01-24" 
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started with the `rarr` Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

Risk assessment is a common component to the project management cycle. The purpose of this package is to assist in the wrangling and presentation of risk assessment data generated throughout the project management cycle. The products created by the functions in this package can be integrated into an R [`bookdown` package] report to create a static webpage to communicate risk during a given project.

## Install

To install the `rarr` package, install from GitHub using the `remotes` package:

```{r install, eval=FALSE}
remotes::install_github(repo = "MVR-GIS/rarr@*release")
```

## Add data

Load the package:

```{r setup}
library(rarr)
```

Load data from data source:

```{r eval=FALSE}

risk<-rarr::db_risk

```

## Wrangle Data

Once the data has been loaded, proceed to the cleaning and wrangle functions.

```{r}
risk_active <- remove_inactive_records(db_risk)
risk <- wrangle_risk(db_risk)

```
