---
title: "Getting started with the `rarr` Package"
author: US Army Corps of Engineers
date: "2023-01-24" 
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started with the `rarr` Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r library, include=FALSE}
library(rarr)
library(magrittr)
library(dplyr)
```

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

Risk assessment is a common component to the project management cycle. The purpose of this package is to assist in the wrangling and presentation of risk assessment data generated throughout the project management cycle. The products created by the functions in this package can be integrated into an R [`bookdown` package] report to create a static webpage to communicate risk during a given project.

## Install

To install the `rarr` package, install from GitHub using the `remotes` package:

```{r install, eval=FALSE}
remotes::install_github(repo = "MVR-GIS/rarr@*release")
```

## Add data

Load the package:

```{r setup, echo= TRUE}
library(rarr)
```

Load data from data source (here we reference internal test data):

```{r eval=FALSE}
risk<-rarr::db_risk
```

## Wrangle Data

Once the data has been loaded, proceed to the cleaning and wrangle functions. The "risk" table will be used as an example.

```{r}
risk_active <- remove_inactive_records(db_risk)
risk <- wrangle_risk(db_risk)

```

Related risk tables must also be wrangled to be able to create the timeline and network analysis figures.

```{r}
rel_action_action<-rarr::wrangle_rel_action_action(db_rel_action_action)

rel_dec_action <- rarr::wrangle_rel_dec_action(db_rel_dec_action)

rel_dec_dec<- rarr::wrangle_rel_dec_dec(db_rel_dec_dec)

```

## Presenting Data

Once the data has been wrangled, it can then be passed into a variety of filters to create tables and figures as seen in [BRIP RARR](https://main.d2tmzs5n6kdoxm.amplifyapp.com/index.html)

Some of these processes involve the [table functions](https://mvr-gis.github.io/rarr/reference/index.html#build-tables) from the `rarr` package and the [figure building functions](https://mvr-gis.github.io/rarr/reference/index.html#build-figures)

### Wrangled output undergoes a filter

```{r high-risk, echo=TRUE, warning=FALSE, message=FALSE}
risk_high <- risk %>%
   dplyr::filter(COST_RISK == "HIGH" | SCHEDULE_RISK == "High" | EFFICACY_RISK == "High")
```

### Example of creating charts with wrangled risk data

```{r echo=TRUE, warning=FALSE, message=FALSE, fig.width=7, fig.height=2, out.width='100%'}
rarr::risk_pies(risk_high)
```

### Example of using a table function to present wrangled risk data
```{r high-risk-register-table, echo=TRUE, warning=FALSE, message=FALSE}
rarr::risk_register_table(risk_high)
```
