---
title: "Building timelines for Risk Reports"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Building timelines for Risk Reports}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r library, include=FALSE}
library(rarr)
library(magrittr)
library(dplyr)
```

The timeline function is can be used to display filtered risk tables and the project timeline. This function requires two functions to create the html timeline widget.

# Create a timevis "data" data frame of risks

In this step the wrangled risk dataframe is wrangled into a risk time data frame.

```{r}
risk<-rarr::db_risk
risk<-rarr::wrangle_risk(risk)
risk_time <- rarr::wrangle_risk_time(risk)
```

# Create a timevis "group" data frame in order to group risks by unique Risk Categories

```{r}
risk_time_riskcategory <- rarr::wrangle_risk_time_riskcat(risk)
```

# Create the project timeline

The final step is to create the p[roject risk timeline. To accomplish this, you input the risk_time and risk_time_riskcategory dataframes into the timeline function and specify the outputs dimensions.

```{r}
rarr::timeline(risk_df = risk_time, 
         groups_df = risk_time_riskcategory,
         height = "700px",
         start = "2021-01-01",
         end = "2025-01-01")
```
