---
title: "Network Analysis in Risk Reports"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Network Analysis in Risk Reports}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r library, include=FALSE}
library(rarr)
library(magrittr)
library(dplyr)
library(igraph)
```


```{r library, include=TRUE}
#Gather Risk Data
db_risk <- rarr::db_risk
db_action <- rarr::db_action
db_decision <- rarr::db_decision

#Wrangle Risk Data
risk <- rarr::wrangle_risk(db_risk)
action <- rarr::wrangle_action(db_action)
decision <- rarr::wrangle_decision(db_decision)

#Gather related items
db_rel_action_action <- rarr::db_rel_action_action
db_rel_dec_dec<- rarr::db_rel_dec_dec
db_rel_dec_action<- rarr::db_rel_dec_action
db_rel_risk_action <- rarr::db_rel_risk_action
db_rel_risk_dec <- rarr::db_rel_risk_dec
db_rel_risk_risk <- rarr::db_rel_risk_risk

#Wrangle related items
rel_action_action <- rarr::wrangle_rel_action_action(db_rel_action_action)
rel_dec_dec <- rarr::wrangle_rel_dec_dec(db_rel_dec_dec)
rel_dec_action <-rarr::wrangle_rel_dec_action(db_rel_dec_action) 
rel_risk_action <-rarr::wrangle_rel_risk_action(db_rel_risk_action)
rel_risk_dec<- rarr::wrangle_rel_risk_dec(db_rel_risk_dec)
rel_risk_risk <-rarr::wrangle_rel_risk_risk(db_rel_risk_risk)

```

# Introduction

The network analysis function creates a related items web that can be beneficial for capturing related risk items. This figure is created by combining an items data frame with a relations dataframe. These items are then passed into an igraph object which is then rendered into the dendrogram html widget.

## Create a dataframe of wrangled risks, actions, and decisions

```{r create-items}
items <- rarr::create_items(risk, action, decision)
```

## Build a dataframe of all wrangled relationships

```{r }
relations<-rarr::create_relations(rel_action_action, rel_dec_action, rel_dec_dec,                          rel_risk_action,rel_risk_dec,rel_risk_risk)
```

## Create igraph object to pass into dendrogram

```{r create network analysis, echo=TRUE}
relate_igraph <- igraph::graph_from_data_frame(d = relations, 
                                               vertices = items, 
                                               directed = FALSE)

```

## Plot network analysis of related items

```{r, echo=TRUE, out.width="90%", dpi = 300}
edgebundleR::edgebundle(relate_igraph, 
                        tension = 0.8, 
                        fontsize = 13,
                        padding = 70)

```

